---
title: "Summary of the pilot data collection"
author: "Adrian Barnett"
date: "2023-06-23"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, comment='', dpi=400)
options(width=1000) # Wide pages
options(scipen=999) # avoid scientific presentation
library(ggplot2)
library(dplyr)
library(flextable)
library(tidyr)
library(stringr)

# data from 0_read_pilot.R
load('data/0_pilot.RData')
```

The pilot was conducted on 23 June 2023.

The table below gives summary statistics on the time taken (in minutes) to complete the Qualtrics questions.

```{r}
both = bind_rows(text, ranks, .id = 'Stage')
stats = group_by(both, Stage) %>%
  select(Stage, duration) %>%
   summarise(n =n(),
             mean = mean(duration, na.rm=TRUE), 
                min = min(duration, na.rm=TRUE),
                max = max(duration, na.rm=TRUE)) %>%
  mutate(Stage = ifelse(Stage == 1, 'First stage - text', 'Second stage - ranking'))
ftab = flextable(stats) %>%
  theme_box() %>%
  colformat_double(j=3:5, digits=1) %>%
  autofit() 
ftab
```

## Stage 1 - attributes, free text 

The table below shows the free text entered by the participants at stage 1. Rank 1 was the most important, and rank 10 the least important.

The question was: "Write an ordered list of the up to 10 attributes you consider most important when submitting a journal article."

Most people gave 10 attributes.

```{r}
text = rename(text,
              'Rank 1' = "q1_13",
              'Rank 2' = "q1_14",
              'Rank 3' = "q1_15",
              'Rank 4' = "q1_16",
              'Rank 5' = "q1_17",
              'Rank 6' = "q1_18",
              'Rank 7' = "q1_19",   
              'Rank 8' = "q1_20",
              'Rank 9' = "q1_21",
              'Rank 10' = "q1_22")
ftab = select(text, -duration) %>%
  flextable() %>%
  theme_box() %>%
  fontsize(size=9, part='all')
ftab
```

APC = article processing charge.

## Stage 2 - attribute rankings

Below we show the average ranks (dots) and the ranges (horizontal lines). There were 18 attributes to choose from.

```{r, fig.width=8, fig.height=8}
# calculate summary stats on the ranks
stats = select(ranks, -duration) %>%
  pivot_longer(cols = everything()) %>%
  mutate(question = as.numeric(str_remove(name, pattern='q2_')),
         question = as.numeric(as.factor(question))) %>% # one question missing
  group_by(question) %>%
  summarise(mean = mean(value),
            min = min(value),
            max = max(value)) 
# add labels
for_plot = ungroup(stats) %>%
  left_join(labels, by='question') %>%
  arrange(-mean) %>%
  mutate(x=1:n()) # ordered row
n_labels = nrow(labels)
#
gplot = ggplot(data = for_plot, aes(x=x, y=mean, ymin=min, ymax=max))+
  geom_point(size=3, col='darkorange2')+
  geom_errorbar(size=1.05, width=0, col='darkorange3')+
  theme_bw()+
  scale_x_continuous(breaks=1:n_labels, labels=for_plot$labels)+
  theme(panel.grid.minor = element_blank(),
        text = element_text(size = 15))+
  ylab('Rank')+
  xlab('')+
  coord_flip()
gplot
```

The higher the rank, the more important it was considered.
