---
title: "Summary of DCE responses (pilot and final sample combined)"
author: "Adrian Barnett"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, comment='', dpi=400)

library(dplyr)
options(dplyr.summarise.inform = FALSE)
library(janitor)
library(flextable)
library(xtable) # for latex tables
library(stringr)
library(readxl)
library(tidyr)
library(visdat) # for missing data
source('99_functions.R')

# graphics set up
library(ggplot2)
library(grid)
library(gridExtra)
g.theme = theme_bw() + theme(panel.grid.minor = element_blank())
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

## get the data, from 5_read_qualtrics.R and 5_read_qualtrics_v2.R
load('data/5_AnalysisReady.RData')
data1 = rename(data, 'q30a' = 'q30', 'q32' = 'q31') # rename questions to match first version
labels1 = labels
load('data/5_AnalysisReady_v2.RData')
data2 = data
labels2 = labels
data = bind_rows(data1, data2, .id = 'sample')
#
load('data/5_sent.RData') # for numbers sent, from 5_emails_sent.R
```

## Recruitment

Plot of recruitment over time.

```{r}
source('6_plot_recruitment_over_time_combined.R')
print(gplot)
# for text
first = min(data$start_date)
last = max(data$start_date)
days_recruit = as.numeric(last - first)
first = format(first, '%d %b %Y')
last = format(last, '%d %b %Y')
```

The total number recruited is `r nrow(data)`. The first participant was recruited on `r first` and the last on `r last`, which is `r days_recruit` days.

## Response rate

```{r}
# total number sent
n_sent = sum(sent$n_sent) # n_sent from 5_emails_sent.R, combine all three approaches

## get data from excel sheet on what happened to emails
dead_or_rejected = read_excel('emails/dead_emails.xlsx', sheet='dead or rejected') %>% 
  select(email) %>% unique() %>% # in case of duplicates
  nrow()
dead_or_rejected_p = round(100*dead_or_rejected/n_sent)
changed = read_excel('emails/dead_emails.xlsx', sheet='changed') %>% 
  nrow()
changed_p = round(100*changed/n_sent)
opt_out = read_excel('emails/dead_emails.xlsx', sheet='opt out') %>% 
  nrow()
opt_out_p = round(100*opt_out/n_sent)
out_of_office = read_excel('emails/dead_emails.xlsx', sheet='out of office') %>% 
  select(email) %>% unique() %>% nrow() # unique because there could be multiple out of office from the same person
out_of_office_p = round(100*out_of_office/n_sent) 
# response rate
response_rate = round(1000*(nrow(data) / (n_sent - dead_or_rejected)))/10
numerator = nrow(data)
denominator = n_sent - dead_or_rejected

```

There were `r dead_or_rejected` (`r dead_or_rejected_p`%) dead or rejected emails.
There were `r changed` (`r changed_p`%) messages with an alternative email for the potential participant.
There were `r opt_out` (`r opt_out_p`%) people who opted out.
There were `r out_of_office` (`r out_of_office_p`%) out of office responses.

After excluding the dead emails, the response rate is `r numerator` out of `r denominator`, which is `r response_rate`%.

## Time taken to answer questions

```{r}
# Move to down with questionnaire completeness? section on question meta-data??
stats = summarise(data,
            Q10 = round(quantile(duration_mins, 0.05)),
            Q25 = round(quantile(duration_mins, 0.25)),
            median = round(median(duration_mins)),
            Q75 = round(quantile(duration_mins, 0.75)),
            Q90 = round(quantile(duration_mins, 0.95)))
#
ftab = flextable(stats) %>%
  theme_box() %>%
  autofit()
ftab
```

The summary statistics show the time in minutes to complete the online questions. Q[x] is the *x*th percentile.

## Questionnaire progress as a percent

The table below shows the questionnaire progress as a percent, with the results grouped into three categories.

```{r}
#
tab = tabyl(data, progress_cat) %>%
  mutate(percent = percent*100)
names(tab)[1] = 'Progress %'
ftab = flextable(tab) %>%
  theme_box() %>%
  colformat_double(j=3, digits=0) %>%
  autofit()
ftab
# for text
finished = sum(data$progress==100)
finished_p = round(100*finished / nrow(data))
```

Most respondents completed most of the questions, but there was a second mode who started but did not progress beyond half-way. The number and percent who finished all the questions was `r finished` (`r finished_p`%).

## How easy or difficult was it to understand the hypothetical choices between journals?

```{r}
n_missing = filter(data, is.na(q24)) %>% nrow() # count number and percent missing
n_missing_p = round(100*n_missing/nrow(data))
tab = filter(data, !is.na(q24)) %>% # exclude missing
  tabyl(q24) %>%
  mutate(percent = percent*100,
         order = case_when(
           q24 == 'Very difficult' ~ 1,
           q24 == 'Difficult' ~ 2,
           q24 == 'Moderate' ~ 3,
           q24 == 'Easy' ~ 4,
           q24 == 'Very easy' ~ 5
         )) %>%
  filter(n > 0) %>%
  arrange(order) %>%
  select(-order)
names(tab)[1] = 'Difficulty'
ftab = flextable(tab) %>%
  theme_box() %>%
  colformat_double(j=3, digits=0) %>%
  autofit()
ftab
```

There were `r n_missing` (`r n_missing_p`%) missing responses.

## What is your broad research area? 

```{r}
n_missing = filter(data, is.na(q25)) %>% nrow() # count number and percent missing
n_missing_p = round(100*n_missing/nrow(data))
tab = filter(data, !is.na(q25)) %>%
  tabyl(q25) %>%
  mutate(percent = percent*100) %>%
  filter(n > 0) %>% # remove zero rows
  arrange(-n)
names(tab)[1] = 'Broad research area'
ftab = flextable(tab) %>%
  theme_box() %>%
  colformat_double(j=3, digits=0) %>%
  autofit()
ftab
```

There were `r n_missing` (`r n_missing_p`%) missing responses.

### What is your broad research area? (other)

```{r}
others = unique(data$q25_8_text)
others = others[!is.na(others)]
print(others)
```


## Gender

```{r}
n_missing = filter(data, is.na(q26)) %>% nrow() # count number and percent missing
n_missing_p = round(100*n_missing/nrow(data))
#
tab = filter(data, !is.na(q26)) %>%
  tabyl(q26) %>%
  mutate(percent = percent*100) %>%
  filter(n > 0)  # remove zero rows
names(tab)[1] = 'Gender'
ftab = flextable(tab) %>%
  theme_box() %>%
  colformat_double(j=3, digits=0) %>%
  autofit()
ftab
```

There were `r n_missing` (`r n_missing_p`%) missing responses.

## Approximately how many years have you been working in research? Answer in terms of working years

```{r}
#
tab  = summarise(data, 
                 missing = sum(is.na(q27)),
                 n = sum(!is.na(q27)),
                 Q1 = round(quantile(q27, 0.25, na.rm=TRUE)),
                 Median = round(quantile(q27, 0.5, na.rm=TRUE)),
                 Q3 = round(quantile(q27, 0.75, na.rm=TRUE)))
ftab = flextable(tab) %>%
  theme_box() %>%
  autofit()
ftab
```

n is the number not missing.

## How many peer-reviewed publications have you published? Include all papers that you are an author on. Include all types of papers, e.g., research articles, commentaries, case reports, etc.

```{r}
tab  = summarise(data, 
                 missing = sum(is.na(q28)),
                 n = sum(!is.na(q28)),
                 Q1 = round(quantile(q28, 0.25, na.rm=TRUE)),
                 Median = round(quantile(q28, 0.5, na.rm=TRUE)),
                 Q3 = round(quantile(q28, 0.75, na.rm=TRUE)))
ftab = flextable(tab) %>%
  theme_box() %>%
  autofit()
ftab
```

n is the number not missing.

## Which country are you currently working in?

```{r}
n_missing = filter(data, is.na(q29)) %>% nrow() # count number and percent missing
n_missing_p = round(100*n_missing/nrow(data))
#
tab = filter(data, !is.na(q29)) %>% # remove missing
  tabyl(q29) %>%
  mutate(percent = round(percent*100)) %>%
  arrange(desc(n)) 
#
names(tab)[1] = 'Country'
ftab = flextable(tab) %>%
  theme_box() %>%
  colformat_double(j=3, digits=0) %>%
  autofit()
ftab
#
text = nrow(tab) # number of countries
# export table to latex - first move to side-by-side so that it fits on page
tab = mutate(tab, percent = ifelse(percent==0, '<1', percent))
m = ceiling(nrow(tab)/2)
split1 = tab[1:m,]
split2 = tab[(m+1):nrow(tab),]
frame = data.frame(Country = '', n = NA, percent= NA) # needed to create balanced columns
split2 = bind_rows(split2, frame)
gap = data.frame(gap=rep('',nrow(split1)))
tab_p = bind_cols(split1, gap, split2)
print(xtable(tab_p, type = "latex", digits=0), file = "results/country_table.tex", include.rownames=FALSE)
```

The total number of countries was `r text`.
There were `r n_missing` (`r n_missing_p`%) missing responses.

## Do you have a target number of publications per year? (tick all that apply)

```{r}
# make tab for tick all
make_tab = filter(data, sample == '2') %>% # only in second sample
  select(id, starts_with('q30')) %>%
  pivot_longer(cols = starts_with('q30')) %>%
  mutate(answer = !is.na(value))
freqs = group_by(make_tab, name) %>% # answers to questions
  summarise(n=n(), r = sum(answer)) %>%
  ungroup
no_answer = group_by(make_tab, id) %>% # people who ticked nothing
  summarise(n=n(), r= sum(answer)) %>%
  filter(r == 0)%>%
  ungroup()
no_answer_frame = data.frame(name = 'No answer', n = nrow(data), r = nrow(no_answer))
# subtract no answer from frequencies
freqs = mutate(freqs,
               n = n - nrow(no_answer))
tab = bind_rows(freqs, no_answer_frame) %>%
  mutate(
               p = round(100*(r / n)),
               cell = paste(r, ' (', p, '%)', sep=''),
               label = case_when(
                 name == 'q30_1' ~ 'Yes, mandatory target from my department or research group',
               name == 'q30_2' ~ 'Yes, suggested target from my department or research group',
               name == 'q30_3' ~ 'Yes, I have a personal target',
               name == 'q30_4' ~ 'No',
               name == 'No answer' ~ 'No answer')) %>%
  select(label, cell) %>%
  rename('Answer' = 'label',
         'n (%)' = 'cell')
#
ftab = flextable(tab) %>%
  theme_box() %>%
  autofit()
ftab
```

This question was only in the second sample.

## What is your target number of publications per year? (skip if none)

```{r}
stats =  filter(data, sample == '2') %>% # only in second sample
  summarise(missing = sum(is.na(q31)),
            n = sum(!is.na(q31)),
            Q10 = round(quantile(q31, 0.05, na.rm = TRUE)),
            Q25 = round(quantile(q31, 0.25, na.rm = TRUE)),
            median = round(median(q31, na.rm = TRUE)),
            Q75 = round(quantile(q31, 0.75, na.rm = TRUE)),
            Q90 = round(quantile(q31, 0.95, na.rm = TRUE)))
#
ftab = flextable(stats) %>%
  theme_box() %>%
  autofit()
ftab
```

n is the number who gave an answer.

This question was only in the second sample.

##### Histogram

```{r}
gplot = ggplot(filter(data, sample == '2'), aes(x= q31))+
  geom_histogram(fill='skyblue', col='grey88')+
  xlab('Target number of publications')+
  g.theme
gplot
```

## Do you have any comments on: our questions, or how you select journals?

The comments are ordered by the longest to shortest. 

```{r comments, results='asis'}
comments = filter(data, 
                  !is.na(q32),
                  q32 != '',
                  !str_detect(tolower(q32), pattern = '^thanks?'),
                  !str_detect(tolower(q32), pattern = '^na$'),
                #  !str_detect(tolower(q32), pattern = '^good luck.?'),
                  !str_detect(tolower(q32), pattern = '^none$'),
                  !str_detect(tolower(q32), pattern = '^no$'),
                  !str_detect(tolower(q32), pattern = '^g$'),
                  !str_detect(tolower(q32), pattern = '^its ok$'),
                  !str_detect(tolower(q32), pattern = '^no comment|^nil$|^good luck.|^ $'),
                  !str_detect(tolower(q32), pattern = '^\\.\\.\\.\\.\\.\\.'),
                  !str_detect(tolower(q32), pattern = '^no further comment'),
                  !str_detect(tolower(q32), pattern = '^no other comment')
                  ) %>%
  mutate(words = str_count(q32, '\\w+'), # word count
         nchar = nchar(q32),
         q32 = str_replace_all(q32, '\n', ' ')) %>% # remove carriage returns
  filter(words > 0) 
# stats on word counts
stats = summarise(comments, 
                  median = round(median(words)), 
                  min = min(words),
                  max = max(words))
#
comments = arrange(comments, -nchar) %>% # longest to shortest - use for final version
  select(q32)
for (k in 1:nrow(comments)){
  cat('* ', comments$q32[k], '\n', sep='')
}
```

There were `r nrow(comments)` comments. The median number of words per comment was `r stats$median` with a range from `r stats$min` to `r stats$max` words.

## Dominant choice set

How many people correctly selected the dominant journal. Missing answers were excluded.

```{r}
tab = filter(data, !is.na(q3)) %>% # exclude missing
  tabyl(q3) %>%
  mutate(percent = round(percent*100),
         correct = case_when(
           q3 == 'Journal A' ~ "Yes",
           q3 == 'Journal B' ~ "No"
         )) %>%
  select(correct, n, percent)
#
names(tab)[1] = 'Correct answer'
ftab = flextable(tab) %>%
  theme_box() %>%
  colformat_double(j=3, digits=0) %>%
  autofit()
ftab
```

## Re-test 

How many people gave the same answer for the re-test choice set. The rows show the original choice set and the columns the re-test. This analysis excludes missing data.

```{r}
make_retest = select(data, sample, id, block, q5, q7, q22)
# retest depends on sample
block_12 = select(make_retest, -q7) %>%
  filter((block %in% c(1,2) & sample==1) | sample ==2) %>%
  rename('original' = 'q5',
         'retest' = 'q22')
block_3 = select(make_retest, -q5) %>%
  filter(block == 3 & sample ==1) %>%
  rename('original' = 'q7',
         'retest' = 'q22')
for_table = bind_rows(block_12, block_3) %>%
  filter(!is.na(original), !is.na(retest))

tab = for_table %>%
  tabyl(original, retest) 
#
names(tab)[1] = 'Original'
ftab = flextable(tab) %>%
  theme_box() %>%
  autofit()
ftab
# for text
agree = round(100*filter(for_table, original == retest) %>% nrow() / nrow(for_table))
```

The agreement between the original and re-test is `r agree`%.

## Missing data

```{r}
# remove variables that cannot be missing
for_missing = select(data, starts_with('q')) %>%
  select(-starts_with('q30_'), -q30a, -q31, -q32, -contains('text')) # comments and questions that were not in both surveys
# for correct ordering of questions in plot
names = names(for_missing)
names = names[order(as.numeric(str_remove(names,'q')))]
for_missing = select(for_missing, names) 
#
mplot = vis_miss(for_missing, cluster=TRUE) + # ar
  theme(legend.position = 'bottom',
        plot.margin = unit(c(0,10,0,0), "mm")) + # bigger space on left, order = top, right, bottom, left
  scale_y_continuous(expand=c(0,0)) +
  ylab('Respondent')
mplot
```

In the above plot the rows are respondents and the columns are the questions. Respondents are grouped according to the pattern in their missing data. 
The amount of item-missing data was small. There was a general increase as the questions increased showing some drop-out (bottom of the plot). Many people did not complete question 31 (publication target number), but this was optional.

The table below shows the question labels.

```{r}
#
for_vis = filter(labels, names %in% names(for_missing)) %>%
mutate(Question = nice_rename(names, version = 2))
#
tab = select(for_vis, names, Question) %>%
  rename('Question\nnumber' = 'names' ) %>%
  flextable() %>%
  theme_alafoli() %>%
  fontsize(size=9, part='all') %>%
  autofit()
tab
```

```{r, include=FALSE}
## export to figure for paper
# use matrix to shorten table
lmatrix = layout_matrix=rbind(c(1,NA),
                             c(1,2),
                             c(1,2),
                             c(1,2),
                             c(1,NA))

#
tabg = flextable::gen_grob(tab) # convert to grob
jpeg('figures/item_missing.jpg', width=7.5, height=5, units='in', quality=100, res=500)
grid.arrange(grobs=list(mplot, tabg), layout_matrix = lmatrix, main=NULL, ncol = 2, widths=c(1.5,1))
invisible(dev.off())
```
