---
title: "Summary of DCE responses"
author: "Adrian Barnett"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, comment='', dpi=400)

library(dplyr)
options(dplyr.summarise.inform = FALSE)
library(janitor)
library(flextable)
library(stringr)
library(readxl)
library(visdat) # for missing data
source('99_functions.R')

# graphics set up
library(ggplot2)
library(grid)
library(gridExtra)
g.theme = theme_bw() + theme(panel.grid.minor = element_blank())
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

# get the data, from 5_read_qualtrics.R
load('data/5_AnalysisReady.RData')
```

## Recruitment

Plot of recruitment over time.

```{r}
source('6_plot_recruitment_over_time.R')
print(gplot)
# for text
first = min(data$start_date)
last = max(data$start_date)
days_recruit = as.numeric(last - first)
first = format(first, '%d %b %Y')
last = format(last, '%d %b %Y')
```

The total number recruited is `r nrow(data)`. The first participant was recruited on `r first` and the last on `r last`, which is `r days_recruit` days.

## Response rate

```{r}
## get data from excel sheet on what happened to emails
dead_or_rejected = read_excel('emails/dead_emails.xlsx', sheet='dead or rejected') %>% nrow()
dead_or_rejected_p = round(100*dead_or_rejected/n_sent)
changed = read_excel('emails/dead_emails.xlsx', sheet='changed') %>% nrow()
changed_p = round(100*changed/n_sent)
opt_out = read_excel('emails/dead_emails.xlsx', sheet='opt out') %>% nrow()
opt_out_p = round(100*opt_out/n_sent)
out_of_office = read_excel('emails/dead_emails.xlsx', sheet='out of office') %>% select(email) %>% unique() %>% nrow() # unique because there could be multiple out of office from the same person
out_of_office_p = round(100*out_of_office/n_sent) # n_sent from 5_read_qualtrics.R
# response rate
response_rate = round(1000*(nrow(data) / (n_sent - dead_or_rejected)))/10
```

There were `r dead_or_rejected` (`r dead_or_rejected_p`%) dead or rejected emails.
There were `r changed` (`r changed_p`%) messages with an alternative email for the potential participant.
There were `r opt_out` (`r opt_out_p`%) people who opted out.
There were `r out_of_office` (`r out_of_office_p`%) out of office responses.

After excluding the dead emails, the response rate is `r response_rate`%.

## Time taken to answer questions

```{r}
# Move to down with questionnaire completeness? section on question meta-data??
stats = summarise(data,
            Q10 = round(quantile(duration_mins, 0.05)),
            Q25 = round(quantile(duration_mins, 0.25)),
            median = round(median(duration_mins)),
            Q75 = round(quantile(duration_mins, 0.75)),
            Q90 = round(quantile(duration_mins, 0.95)))
#
ftab = flextable(stats) %>%
  theme_box() %>%
  autofit()
ftab
```

The summary statistics show the time in minutes to complete the online questions. Q[x] is the *x*th percentile.

## Questionnaire progress as a percent

The table below shows the questionnaire progress as a percent, with the results grouped into three categories.

```{r}
#
tab = tabyl(data, progress_cat) 
names(tab)[1] = 'Progress %'
ftab = flextable(tab) %>%
  theme_box() %>%
  colformat_double(j=3, digits=0) %>%
  autofit()
ftab
# for text
finished = sum(data$progress==100)
finished_p = round(100*finished / nrow(data))
```

All respondents completed most of the questions. The number and percent who finished all the questions was `r finished` (`r finished_p`%).

## How easy or difficult was it to understand the hypothetical choices between journals?

```{r}
tab = mutate(data, q24 = ifelse(is.na(q24), 'Missing', q24)) %>%
  tabyl(q24) %>%
  mutate(percent = percent*100,
         order = case_when(
           q24 == 'Very difficult' ~ 1,
           q24 == 'Difficult' ~ 2,
           q24 == 'Moderate' ~ 3,
           q24 == 'Easy' ~ 4,
           q24 == 'Very easy' ~ 5
         )) %>%
  filter(n > 0) %>%
  arrange(order) %>%
  select(-order)
names(tab)[1] = 'Difficulty'
ftab = flextable(tab) %>%
  theme_box() %>%
  colformat_double(j=3, digits=0) %>%
  autofit()
ftab
```

## What is your broad research area? 

```{r}
tab = mutate(data, q25 = ifelse(is.na(q25), 'Missing', q25)) %>%
  tabyl(q25) %>%
  mutate(percent = percent*100) %>%
  filter(n > 0) %>% # remove zero rows
  arrange(-n)
names(tab)[1] = 'Broad research area'
ftab = flextable(tab) %>%
  theme_box() %>%
  colformat_double(j=3, digits=0) %>%
  autofit()
ftab
```

### What is your broad research area? (other)

```{r}
others = unique(data$q25_8_text)
others = others[!is.na(others)]
print(others)
```


## Gender

```{r}
tab = mutate(data, q26 = ifelse(is.na(q26), 'Missing', q26)) %>%
  tabyl(q26) %>%
  mutate(percent = percent*100) %>%
  filter(n > 0)  # remove zero rows
names(tab)[1] = 'Gender'
ftab = flextable(tab) %>%
  theme_box() %>%
  colformat_double(j=3, digits=0) %>%
  autofit()
ftab
```

## Approximately how many years have you been working in research? Answer in terms of working years

```{r}
tab  = summarise(data, 
                 missing = sum(is.na(q27)),
                 Q1 = round(quantile(q27, 0.25, na.rm=TRUE)),
                 Median = round(quantile(q27, 0.5, na.rm=TRUE)),
                 Q3 = round(quantile(q27, 0.75, na.rm=TRUE)))
ftab = flextable(tab) %>%
  theme_box() %>%
  autofit()
ftab
```

## How many peer-reviewed publications have you published? Include all papers that you are an author on. Include all types of papers, e.g., research articles, commentaries, case reports, etc.

```{r}
tab  = summarise(data, 
                 missing = sum(is.na(q28)),
                 Q1 = round(quantile(q28, 0.25, na.rm=TRUE)),
                 Median = round(quantile(q28, 0.5, na.rm=TRUE)),
                 Q3 = round(quantile(q28, 0.75, na.rm=TRUE)))
ftab = flextable(tab) %>%
  theme_box() %>%
  autofit()
ftab
```

## Which country are you currently working in?

```{r}
tab = mutate(data, q29 = ifelse(is.na(q29), 'Missing', q29)) %>% # replace missing
  tabyl(q29) %>%
  mutate(percent = round(percent*100)) %>%
  arrange(desc(n))
# combine countries that are under 5 (changed to 1 for now)
combine_number = 0
not_small = filter(tab, n > combine_number)
small = filter(tab, n <= combine_number) %>%
  summarise(n = sum(n),
            percent = sum(percent)) %>%
  mutate(q29 = 'Other')
tab = bind_rows(not_small, small)
#
names(tab)[1] = 'Country'
ftab = flextable(tab) %>%
  theme_box() %>%
  colformat_double(j=3, digits=0) %>%
  autofit()
ftab
```

## Please give your agreement with this statement: My department's or research group's expectations with respect to publishing are reasonable

```{r}
tab = mutate(data, q30 = ifelse(is.na(q30), 'Missing', q30)) %>%
  tabyl(q30) %>%
  mutate(percent = percent*100,
         order = case_when(
           q30 == 'Strongly disagree' ~ 1,
           q30 == 'Disagree' ~ 2,
           q30 == 'Neither agree nor disagree' ~ 3,
           q30 == 'Agree' ~ 4,
           q30 == 'Strongly agree' ~ 5
         )) %>%
  filter(n > 0) %>%
  arrange(order) %>%
  select(-order)
names(tab)[1] = 'Agreement'
ftab = flextable(tab) %>%
  theme_box() %>%
  colformat_double(j=3, digits=0) %>%
  autofit()
ftab
```

## Do you have any comments on: our questions, or how you select journals?

The comments are ordered by the longest to shortest. 

```{r comments, results='asis'}
comments = filter(data, 
                  !is.na(q31),
                 # !str_detect(tolower(q31), pattern = '^thank'),
                  !str_detect(tolower(q31), pattern = '^na$'),
                #  !str_detect(tolower(q31), pattern = '^good luck.?'),
                  !str_detect(tolower(q31), pattern = '^none$'),
                  !str_detect(tolower(q31), pattern = '^no$'),
                  !str_detect(tolower(q31), pattern = '^no comment'),
                  !str_detect(tolower(q31), pattern = '^\\.\\.\\.\\.\\.\\.'),
                  !str_detect(tolower(q31), pattern = '^no further comment'),
                  !str_detect(tolower(q31), pattern = '^no other comment')
                  ) %>%
  mutate(words = str_count(q31, '\\w+'), # word count
         nchar = nchar(q31))
# stats on word counts
stats = summarise(comments, 
                  median = round(median(words)), 
                  min = min(words),
                  max = max(words))
#
comments = arrange(comments, -nchar) %>% # longest to shortest - use for final version
  select(q31)
for (k in 1:nrow(comments)){
  cat('* ', comments$q31[k], '\n', sep='')
}
```

The median number of words per comment was `r stats$median` with a range from `r stats$min` to `r stats$max` words.

## Dominant choice set

How many people correctly selected the dominant journal.

```{r}
tab = mutate(data, q3 = ifelse(is.na(q3), 'Missing', q3)) %>% # replace missing
  tabyl(q3) %>%
  mutate(percent = round(percent*100),
         correct = case_when(
           q3 == 'Journal A' ~ "Yes",
           q3 == 'Journal A' ~ "No"
         )) %>%
  select(correct, n, percent)
#
names(tab)[1] = 'Correct answer'
ftab = flextable(tab) %>%
  theme_box() %>%
  colformat_double(j=3, digits=0) %>%
  autofit()
ftab
```

## Re-test 

How many people gave the same answer for the re-test choice set. The rows show the original choice set and the columns the re-test. This analysis excludes missing data.

```{r}
make_retest = select(data, id, block, q5, q7, q22)
block_12 = select(make_retest, -q7) %>%
  filter(block %in% c(1,2)) %>%
  rename('original' = 'q5',
         'retest' = 'q22')
block_3 = select(make_retest, -q5) %>%
  filter(block == 3) %>%
  rename('original' = 'q7',
         'retest' = 'q22')
for_table = bind_rows(block_12, block_3) %>%
  filter(!is.na(original), !is.na(retest))

tab = for_table %>%
  tabyl(original, retest) 
#
names(tab)[1] = 'Original'
ftab = flextable(tab) %>%
  theme_box() %>%
  autofit()
ftab
# for text
agree = round(100*filter(for_table, original == retest) %>% nrow() / nrow(for_table))
```

The agreement between the original and re-test is `r agree`%.

## Missing data

```{r}
# remove variables that cannot be missing
for_missing = select(data, starts_with('q')) %>%
  select(-q31, -contains('text')) # comments
# add labels
for_vis = filter(labels, names %in% names(for_missing)) %>%
  mutate(label_nice = nice_rename(names))
xbreaks = for_vis$names
xlabels = for_vis$label_nice
#
mplot = vis_dat(for_missing, sort_type = FALSE) +
  theme(legend.position = 'bottom',
        plot.title = element_text(margin = margin(0,0,-10,0))) + # reduce space between title and plot
  scale_y_continuous(expand=c(0,0)) +
 # scale_x_discrete(breaks = xbreaks)+#, labels = xlabels)+ # not working
  ylab('Respondent')
mplot
```

The amount of item-missing data was small. The table below shows the question labels.

```{r}
tab = select(for_vis, names, label_nice) %>%
  rename('question' = 'names', 'label' = 'label_nice') %>%
  flextable() %>%
  theme_alafoli() %>%
  fontsize(size=9, part='all') %>%
  autofit()
tab
```
